MS_Intro_Short

### 2024-02-21 Markdown/Manuscript/Child_RMDs/MS_Imp_Example.Rmd
up to example

Our CHEMs are being derived from and applied to real data (which can be empirical, simulated or assumption, so long as it is appropriate for use in analysis intended to inform decision-making) from Australia. To help demonstrate the potential use of CHEMs in other decision contexts, we also create toy datasets. Data created for illustration purposes is prominently labelled as not for use in decision-analysis.

@@

>>>>

@@

## Online services
To track our code coverage, we linked our GitHub organisation to an account we established at codecov [@codecov_2022]. The framework also supports integrations with the open science repositories Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] that provide persistent storage solutions that generate a Digital Object Identifier (DOI) for each code and data collection.

The third party services that our framework is designed to work with include GitHub, Zenodo, Dataverse,
codecov [@codecov_2022]

We created a GitHub organisation (a collection of code repositories) where source code that we author is stored and version controlled. We configured individual repositories in our GitHub organisation to implement continuous integration. By default, code libraries authored with our framework will use continuous integration to assess compliance with policies specified by the Comprehensive R Archive Network (CRAN) [@CRAN2022]. To track our code coverage, we linked our GitHub organisation to an account we established at codecov [@codecov_2022]. To facilitate the creation and hosting of documentation websites, we enabled GitHub Pages in each repository used for code library development.

We also created a Zenodo community - a collection of permanent, uniquely identified repositories. We then linked our Zenodo community and GitHub organisation so that every time we specify a version of code in one of our GitHub repositories as a “release”, a copy of that code is automatically created on Zenodo with a DOI. Finally, to manage model datasets, we created a dedicated collection within the Harvard Dataverse installation.

## Documentation website
We used functions from our foundation framework library to partially automate website updates relating to available CHEM modules, datasets and analysis programs.

### 2024-02-21 Markdown/Manuscript/Child_RMDs/MS_Imp_Motivation.Rmd
up to example

## Economic topics
Initially, we plan to construct readyforwhatsnext from projects in four of the twelve domains of health economics identified by Wagstaff and Culyer [@wagstaff2012four]:

@@

Potential future directions are to incorporate projects in two additional Wagstaff and Culyer domains of: (i) public health (to model the impact of selected fiscal policy and regulation options on young people's mental health); and (ii) human resources (to model the supply and behaviours of the youth mental health workforce). Our ultimate aim is for readyforwhatsnext to flexibly combine its constituent parts in analyses that help answer questions in two additional Wagstaff and Culyer domains:

@@

A high level schematic of how we aim to implement readyforwhatsnext as a modular and open source CHEM to address these topics is outlined in Figure \@ref(fig:fig1).

## Transferability
Although we are principally interested in using readyforwhatsnext to answer policy questions relating to the mental health of young people in Australia, we want to facilitate model transfer to other jurisdictions. We believe that a good starting point for facilitating model transferable is to develop a CHEM that is relatively easy to understand, use and adapt. For that reason, the transferability requirements we specified for readyforwhatsnext are to meet six explicit criteria for transparency, reusability and updatability. We have describe these criteria and theire relationship to ethical modelling practice elsewhere [@ethicsCHEMS2024], but briefly they are:

@@

T4) Licenses restrict permit derivative works; <!-- rephrase Liceses permit derivative works-->

@@

>>>>

## Economic topics
Initially, we are constructing readyforwhatsnext from projects in four of the twelve domains of health economics identified by Wagstaff and Culyer [@wagstaff2012four]:

@@

Potential future directions could incorporate projects in two additional Wagstaff and Culyer domains of: (i) public health (to model the impact of selected fiscal policy and regulation options on young people's mental health); and (ii) human resources (to model the supply and behaviours of the youth mental health workforce). Our ultimate aim is for readyforwhatsnext to flexibly combine its constituent parts in analyses that help answer questions in two additional Wagstaff and Culyer domains:

@@

## Transferability
Although we are principally interested in using readyforwhatsnext to answer policy questions relating to the mental health of young people in Australia, we want to facilitate model transfer to other jurisdictions. The transferability requirements we have specified for readyforwhatsnext are to meet six explicit criteria for transparency, reusability and updatability. We have describe these criteria and their relationship to ethical modelling practice elsewhere [@ethicsCHEMS2024], but briefly they are:

@@

T4) Licenses permit derivative works; <!-- rephrase Liceses permit derivative works-->

@@

The readyforwhatsnext model is being derived from and applied to real Australian data (which can be empirical, simulated or assumption, so long as it is appropriate for use in analysis intended to inform decision-making). To help demonstrate the potential transferability of readyforwhatsnext to other decision contexts, we are also creating toy datasets. Toy data created for illustration purposes will be prominently labelled as not for use in decision-analysis.

A high level schematic guiding our implementation of readyforwhatsnext as a modular and open source CHEM is outlined in Figure \@ref(fig:fig1).

### 2024-02-21 Markdown/Manuscript/Child_RMDs/MS_Imp_Toolkit.Rmd
up to example

We decided to develop a software framework to help us address challenges we encountered during the planning and early implementation of readyforwhatsnext. The software framework is called ready4 [@ready424].

## User requirements
We created ready4 with one primary user group in mind - ourselves. The user requirements (URs) for ready4 evolved over six years (2018-2024) as we became aware of new challenges in implementing readyforwhatsnext that we needed to solve. We specified these user requirements in terms that facilitate solutions that may meet the needs of two other CHEM developers. Currently, these requirements are:

UR 1) A *template* for creating CHEM modules that can: (i) safely share inputs and outputs with each other without impairing any module's integrity; (ii) be run as independent models; and (iii) be selectively replaced, updated or extended.

@@

UR 3) A *syntax* that promotes simplicity and consistency in how algorithms associated with CHEM modules are described and used in health economic analysis programs.

@@

###	Online services 
Framework libraries are designed to be used in conjunction with a number of third-party online services that users of the framework will need to establish and configure accounts with.

We created a GitHub organisation (a collection of code repositories) where source code that we author is stored and version controlled. We configured individual repositories in our GitHub organisation to implement continuous integration. By default, code libraries authored with our framework will use continuous integration to assess compliance with policies specified by the Comprehensive R Archive Network (CRAN) [@CRAN2022]. To track our code coverage, we linked our GitHub organisation to an account we established at codecov [@codecov_2022]. To facilitate the creation and hosting of documentation websites, we enabled GitHub Pages in each repository used for code library development.

We also created a Zenodo community - a collection of permanent, uniquely identified repositories. We then linked our Zenodo community and GitHub organisation so that every time we specify a version of code in one of our GitHub repositories as a “release”, a copy of that code is automatically created on Zenodo with a DOI. Finally, to manage model datasets, we created a dedicated collection within the Harvard Dataverse installation.

###	Documentation website
We developed a framework documentation website (https://www.ready4-dev.com) that provides guidance to model developers on how to use and contribute improvements to the ready4 software framework and CHEM modules developed with it. The documentation website is versioned, which means documentation relating to prior versions of framework software can be archived, retrieved and viewed.

The documentation website was developed using the Hugo framework [@hugo_2023], Docsy theme [@docsy_2023] and Algolia DocSearch [@algoliadocsearch_2023] and is hosted using the Netlify [@netlify_2023] service.  We used functions from our foundation framework library to partially automate website updates relating to available CHEM modules, datasets and analysis programs. We linked our Netlify account to our GitHub organisation so that the project website would automatically update whenever its  source code (publicly available in a GitHub repository) was edited.

>>>>

We began developing a prototype software framework in order to address a number of challenges we encountered during the planning and early implementation of readyforwhatsnext. The software framework is called ready4.

## User requirements
We created ready4 with one primary user group in mind - ourselves. The user requirements (URs) for ready4 evolved over six years (2018-2024) as we became aware of new issues that we needed to solve. Currently, these requirements are:

UR 1) A *template module* for use in CHEM implementations in which modules can: (i) be run as independent models; (ii) safely combined, sharing inputs and outputs with each other without unintended interference; and (iii) be selectively replaced, updated or extended.

@@

UR 3) A *programming syntax* that promotes simplicity and consistency in how algorithms associated with CHEM modules are described and used in health economic analysis programs.

@@

###	Online services 
Framework libraries are designed to be used in conjunction with a number of third-party online services that users of ready4 will need to establish and configure accounts with. The framework's developer tools integrate with online code development, testing and archiving services. The ready4 framework uses the GitHub [@github2007] service's tools for: software development, testing, version control and distribution; hosting of documentation websites; and transparent record keeping of collaborator contributions. A useful concept for informing software users about the extensiveness of testing procedures is code coverage [@ERICWONG2010188] - the proportion of code that has been explicitly tested. The ready4 framework uses the codecov [@codecov_2022] service to measure and share information about code coverage. The open science repository service Zenodo [@Zenodo2013] is used to provide persistent storage, uniquely identified with a a Digital Object Identifier (DOI), of each code release.

The framework's data management tools use the Dataverse [@Dataverse2007] data repository service for persistent, uniquely identifiable and versioned storage of model input and output data. For the management of frequently updated datasets that do not require persistent storage, ready4 uses GitHub.

###	Documentation website
We developed a framework documentation website (https://www.ready4-dev.com) that provides guidance to model developers on how to use and contribute improvements to the ready4 software framework and CHEM modules developed with it. The documentation website is versioned, which means documentation relating to prior versions of framework software can be archived, retrieved and viewed. The documentation website was developed using the Hugo framework [@hugo_2023], Docsy theme [@docsy_2023] and Algolia DocSearch [@algoliadocsearch_2023] and is hosted using the Netlify [@netlify_2023] service.  We linked our Netlify account to our GitHub organisation so that the project website would automatically update whenever its source code (publicly available in a GitHub repository) was edited.

### 2024-02-21 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
up to example

Some of the barriers<!-- Give examples --> to the development of open-source and modular CHEMs may be amenable to technical solutions such as software frameworks.<!-- Check last sentence was not used in ethics manuscript  --> A software framework is a shared common technology used by developers to collaboratively author software and which is not typically visible to software end-users [@myllarniemi2018development]. A software framework provides a foundation for developing multiple software applications with shared resources (e.g., code and data files), that can be modified to suit specific needs. Advantages of using software frameworks include facilitating code reuse and extension, promoting good programming practice and the capability to provide enhanced functionality and performance without additional effort by developers [@edwin2014software]. Software frameworks have widely been developed and implemented in data science, for example, PyTorch [@PyTorch2019] for machine learning using Python. However, software frameworks can be challenging and time consuming to create and may become excessively complex over time [@edwin2014software]. Software frameworks can also be difficult to learn, often requiring model developers to undergo specialist training [@myllarniemi2018development].

>>>>

Some of the technical barriers<!-- Give examples --> to the development of open-source and modular CHEMs could be addressed by appropriate software frameworks.<!-- Check last sentence was not used in ethics manuscript  --> A software framework is a shared common technology used by developers to collaboratively author software and which is not typically visible to software end-users [@myllarniemi2018development]. A software framework provides a foundation for developing multiple software applications with shared resources (e.g., code and data files), that can be modified to suit specific needs. Advantages of using software frameworks include facilitating code reuse and extension, promoting good programming practice and the capability to provide enhanced functionality and performance without additional effort by developers [@edwin2014software]. Software frameworks have widely been developed and implemented in data science, for example, PyTorch [@PyTorch2019] for machine learning using Python. However, software frameworks can be challenging and time consuming to create and may become excessively complex over time [@edwin2014software]. Software frameworks can also be difficult to learn, often requiring model developers to undergo specialist training [@myllarniemi2018development].
